Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-19 RR_manuscript/Draft_RR.Rmd
add author affiliations

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

- name: Wood Drake

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

- name: Westerbeek Hans

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

- name: Julio César López Otero

@@

@@

@@

- name: Carol-Ann McConnellogue

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

- name: Koolen Ruud

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

- name: Kingsley Ugwuanyi

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

- num: 1

@@

- num: 2
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany

@@

  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States

@@

  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Timo B. Roettger"
email: "timo.b.roettger@iln.uio.no"
abstract: "Recent empirical studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior. In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question, resulting in substantial variability in reported effect sizes and their interpretation. Using Bayesian meta-analytic tools, we further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses. In light of this idiosyncratic variability, we recommend that researchers more transparently share details of their analysis, strengthen the link between theoretical construct and quantitative system and calibrate their (un)certainty in their conclusions"
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    template: template.tex
    includes:
      in_header: preamble.tex

>>>>

  num: 5
- name: Byron Ahn
  num: 6

@@

  num: 7

@@

  num: 8

@@

  num: 9

@@

  num: 10

@@

  num: 11

@@

  num: 12

@@

  num: 13

@@

  num: 14

@@

  num: 15

@@

  num: 16

@@

  num: 17

@@

  num: 18

@@

  num: 19

@@

  num: 20

@@

  num: 21

@@

  num: 22

@@

  num: 23

@@

  num: 24

@@

  num: 25

@@

  num: 26

@@

  num: 27

@@

  num: 28

@@

  num: 29

@@

  num: 30

@@

  num: 31

@@

  num: 32

@@

  num: 33

@@

  num: 34

@@

  num: 35

@@

  num: 36

@@

  num: 37

@@

  num: 38

@@

  num: 39

@@

  num: 40

@@

  num: 41

@@

  num: 42

@@

  num: 43

@@

  num: 44

@@

  num: 45
- name: Shiloh Drake
  num: 46

@@

  num: 47

@@

  num: 48

@@

  num: 49

@@

  num: 50

@@

  num: 51

@@

  num: 52

@@

  num: 53

@@

  num: 54

@@

  num: 55

@@

  num: 56

@@

  num: 57

@@

  num: 58

@@

  num: 59

@@

  num: 60

@@

  num: 61

@@

  num: 62

@@

  num: 63

@@

  num: 64

@@

  num: 65

@@

  num: 66

@@

  num: 67

@@

  num: 68

@@

  num: 69

@@

  num: 70

@@

  num: 71

@@

  num: 72

@@

  num: 73

@@

  num: 74

@@

  num: 75

@@

  num: 76

@@

  num: 77

@@

  num: 78

@@

  num: 79

@@

  num: 80

@@

  num: 81

@@

  num: 82

@@

  num: 83

@@

  num: 84

@@

  num: 85

@@

  num: 86

@@

  num: 87

@@

  num: 88
- name: Thomas Kettig
  num: 89

@@

  num: 90
- name: Ruud Koolen
  num: 91

@@

  num: 92

@@

  num: 93

@@

  num: 94

@@

  num: 95

@@

  num: 96

@@

  num: 97

@@

  num: 98

@@

  num: 99

@@

  num: 100

@@

  num: 101

@@

  num: 102
- name: Julio Cesar Lopez Otero
  num: 103

@@

  num: 104

@@

  num: 105

@@

  num: 106
- name: Carol-Ann Mary McConnellogue
  num: 107

@@

  num: 108

@@

  num: 109

@@

  num: 110

@@

  num: 111

@@

  num: 112

@@

  num: 113

@@

  num: 114

@@

  num: 115

@@

  num: 116

@@

  num: 117

@@

  num: 118

@@

  num: 119

@@

  num: 120

@@

  num: 121

@@

  num: 122

@@

  num: 123

@@

  num: 124

@@

  num: 125

@@

  num: 126

@@

  num: 127

@@

  num: 128

@@

  num: 129

@@

  num: 130

@@

  num: 131

@@

  num: 132

@@

  num: 133

@@

  num: 134

@@

  num: 135

@@

  num: 136

@@

  num: 137

@@

  num: 138
- name: Kingsley O. Ugwuanyi
  num: 139

@@

  num: 140

@@

  num: 141

@@

  num: 142

@@

  num: 143

@@

  num: 144

@@

  num: 145

@@

  num: 146
- name: Hans Westerbeek
  num: 147

@@

  num: 148

@@

  num: 149

@@

  num: 150

@@

  num: 151

@@

  num: 152

@@

  num: 153

@@

  num: 154

@@

  num: 155

@@

  num: 156

@@

  num: 157

@@

  num: 158

@@

- num: 1, 2

@@

@@

  org: Department of Spanish and Portuguese, Rutgers University, United States

@@

  org: Department of Linguistics, Cornell University, United States
- num: 5
  org: Department of General and Computational Linguistics, University of Tübingen, Germany
- num: 6
  org: Program in Linguistics, Princeton University, United States
- num: 7
  org: Jubail English Language and Preparatory Year Institute, Royal Commission for Jubail and Yanbu, Saudi Arabia
- num: 8
  org: Laboratoire de Lingusitique Formelle (LLF), CNRS, Université Paris Cité, France
- num: 9
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 10
  org: Department of Linguistics, University of Arizona, United States
- num: 11
  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
- num: 12
  org: Departamento de Letras, Universidade Federal de São Carlos, Brazil
- num: 13
  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
- num: 14
  org: Department of Linguistics, University of Oregon, United States
- num: 15
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 16
  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
- num: 17
  org: Department of Psychology, University of California, Davis, United States
- num: 18
  org: Department of Linguistics, University of Arizona, United States
- num: 19
  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
- num: 20
  org: NA, University of Pennsylvania, United States
- num: 21
  org: Department of Communication Sciences and Disorders, Syracuse University, United States
- num: 22
  org: Department of Spanish, Villanova University, United States
- num: 23
  org: Department of English Language and Linguistics, University of Birmingham, United Kingdom
- num: 24
  org: Department of Philosophy, Carnegie Mellon University, United States
- num: 25
  org: Department of Spanish & French Studies, Occidental College, United States
- num: 26
  org: Department of English, Texas Tech University, United States
- num: 27
  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
- num: 28
  org: Department of Spanish and Portuguese, University of Arizona, United States
- num: 29
  org: Division of Mathematics and Computer Science, Simmons University, United States
- num: 30
  org: Analytics, Harrisburg University of Science and Technology, United States
- num: 31
  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
- num: 32
  org: Department of Psychology, University at Buffalo, SUNY, United States
- num: 33
  org: Université Paris Cité, France
- num: 34
  org: IfL-Phonetik, University of Cologne, Germany
- num: 35
  org: Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom
- num: 36
  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
- num: 37
  org: Basque Center on Cognition Brain and Language, Spain
- num: 38
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 39
  org: Department of Linguistics, University of California, Davis, United States
- num: 40
  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
- num: 41
  org: LLING, UMR6310, Nantes Université / CNRS, France
- num: 42
  org: Department of Linguisticss and TESOL, University of Texas at Arlington, United States
- num: 43
  org: School of Psychology, Newcastle University, United Kingdom
- num: 44
  org: Department of Linguistics, University of Oregon, United States
- num: 45
  org: School of Psychological Sciences and Health, University of Strathclyde, United Kingdom
- num: 46
  org: Department of Linguistics, University of Oregon, United States
- num: 47
  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
- num: 48
  org: Department of comparative language science, Universität Zürich, Swizerland, Switzerland
- num: 49
  org: Basque Center on Cognition Brain and Language, Spain
- num: 50
  org: Department of Linguistics, University of Canterbury, New Zealand
- num: 51
  org: IKER (UMR 5478), Centre National de la Recherche Scientifique (CNRS), France
- num: 52
  org: Department of Neuroscience, Psychology and Behaviour, University of Leicester, United Kingdom
- num: 53
  org: Statistics Group, Association for Diversity in Linguistics, Germany
- num: 54
  org: CLILLAC-ARP, Université Paris Cité, France
- num: 55
  org: Department of Psychology, University of California, Davis, United States
- num: 56
  org: Department of Music, Max Planck Institute for Empirical Aesthetics, Germany
- num: 57
  org: Department of Psychology, Pacific Lutheran University, United States
- num: 58
  org: Department of Linguistics, University of Oregon, United States
- num: 59
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 60
  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
- num: 61
  org: Department of languages, linguistics, and translation, Université Laval, Canada
- num: 62
  org: New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand
- num: 63
  org: Department of Languages, Literatures, and Cultures, Saint Louis University, United States
- num: 64
  org: Department of Psychology, Princeton University, United States
- num: 65
  org: LPC, Aix Marseille Univ, CNRS, France
- num: 66
  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
- num: 67
  org: IfL-Phonetik, University of Cologne, Germany
- num: 68
  org: Department of English Language and Linguistics, University of Birmingham, United Kingdom
- num: 69
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 70
  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
- num: 71
  org: Department of Linguistics and TESOL, University of Texas at Arlington, United States
- num: 72
  org: New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand
- num: 73
  org: Ao Tawhiti Unlimited Discovery, New Zealand
- num: 74
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 75
  org: Department of Speech, Language, and Hearing Sciences, University of Colorado Boulder, United States
- num: 76
  org: Department of Linguistics and Cognitive Science, Pomona College, United States
- num: 77
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 78
  org: University of California, Los Angeles, United States
- num: 79
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 80
  org: Department of Modern and Classical Languages and Literatures, California State University, Northridge, United States
- num: 81
  org: School of Psychology, University of Birmingham, United Kingdom
- num: 82
  org: School of Humanities, Language and Global Studies, University of Central Lancashire, United Kingdom
- num: 83
  org: Department of Linguistics, University of Canterbury, Aotearoa
- num: 84
  org: Programa de Pós-Graduação em Letras, Federal University of Rio Grande do Sul, Brazil
- num: 85
  org: Department of Linguistics, University of Canterbury, New Zealand
- num: 86
  org: Institute of Linguistics, University of Cologne, Germany
- num: 87
  org: Department of Linguistics, University of Washington, United States
- num: 88
  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
- num: 89
  org: Department of Language and Linguistic Science, University of York, United Kingdom
- num: 90
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 91
  org: Department of Communication and Cognition, Tilburg University, Netherlands
- num: 92
  org: Department of Communication and Cognition, Tilburg University, the Netherlands
- num: 93
  org: Department of Linguistics and Basque Studies, University of the Basque Country UPV/EHU, Spain
- num: 94
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 95
  org: Department of Psychology, Bowdoin College, ME, United States
- num: 96
  org: Linguistic Convergence Laboratory, HSE University, Russia
- num: 97
  org: Department of Communication and Cognition, Tilburg University, the Netherlands
- num: 98
  org: School of Psychology, University of Birmingham, United Kingdom
- num: 99
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 100
  org: Institute of German Language I Linguistics, University of Cologne, Germany
- num: 101
  org: Department of English Language Studies, Federal University of Ceará, Brazil
- num: 102
  org: Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom
- num: 103
  org: Department of Hispanic Studies, University of Houston, United States
- num: 104
  org: Department of English and American Studies, University of Salzburg, Austria
- num: 105
  org: School of Linguistics & Language Studies, Carleton University, Canada
- num: 106
  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
- num: 107
  org: Population Health Sciences Institute - Faculty of Medical Sciences, Newcastle University, United Kingdom
- num: 108
  org: HSE University, Russia
- num: 109
  org: Speech and Language Therapy, University of Strathclyde, United Kingdom
- num: 110
  org: LPC, Aix Marseille Univ, CNRS, France
- num: 111
  org: Department of Psychology, Faculty of Media and Communications, Singidunum University, Serbia
- num: 112
  org: Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany
- num: 113
  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
- num: 114
  org: Graduate Program in Linguistics, Federal University of Ceará, Brazil
- num: 115
  org: World Languages, Literatures and Cultures Department, University of Arkansas, United States
- num: 116
  org: Deparment of Linguistics, Queen Mary University of London, United Kingdom
- num: 117
  org: CLILLAC-ARP, Université Paris Cité, France
- num: 118
  org: Department of Linguistics, University of Alberta, Canada
- num: 119
  org: Department of Linguistics, University of California, Berkeley, United States
- num: 120
  org: Department of Linguistics, Macquarie University, Australia
- num: 121
  org: Center for Cognitive Science, Rutgers University, United States
- num: 122
  org: Department of Spanish and Portuguese, Rutgers University, United States
- num: 123
  org: Department of Speech, Language, and Hearing Sciences, Saint Louis University, United States
- num: 124
  org: Department of Psychology, Witten/Herdecke University, Germany
- num: 125
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 126
  org: Department of Linguistics, University of Colorado Boulder, United States
- num: 127
  org: Clinical Audiology, Speech and Language (CASL) Research Centre, Queen Margaret University Edinburgh, United Kingdom
- num: 128
  org: Department of English and American Studies, University of Salzburg, Austria
- num: 129
  org: Department of English and American Studies, Heinrich Heine University Düsseldorf, Germany
- num: 130
  org: Linguistic Convergence Laboratory, HSE University, Russia
- num: 131
  org: Department of Linguistics, University of British Columbia, Canada
- num: 132
  org: Department of Psychiatry and Psychotherapy, University Hospital Cologne, Germany
- num: 133
  org: Department of Linguistics, Brigham Young University, United States
- num: 134
  org: Department of Linguistics, University of Colorado Boulder, United States
- num: 135
  org: Department of Neuroscience, Max Planck Institute for Empirical Aesthetics, Germany
- num: 136
  org: Department of General Linguistics, University of Tübingen, Germany
- num: 137
  org: Department of Linguistics, University of Alberta, Canada
- num: 138
  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
- num: 139
  org: Department of English & Literary Studies, University of Nigeria, Nsukka, Nigeria
- num: 140
  org: IKER-UMR5478, Centre National de la Recherche Scientifique (CNRS), France
- num: 141
  org: Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany
- num: 142
  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
- num: 143
  org: Department of Communication and Cognition, Tilburg University, the Netherlands
- num: 144
  org: Chinese and Bilingual Studies, Hong Kong Polytechnic University, Hong Kong SAR, China
- num: 145
  org: Department of Linguistics, University of Arizona, United States
- num: 146
  org: IfL-Phonetik, University of Cologne, Germany
- num: 147
  org: Department of Languages, Literature and Communication, Utrecht University, Netherlands
- num: 148
  org: Department of Modern Languages, Carnegie Mellon University, United States
- num: 149
  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
- num: 150
  org: Geospatial Research Institute, University of Canterbury, New Zealand
- num: 151
  org: Department of Linguistics, University of Oregon, United States
- num: 152
  org: Département de Lettres modernes, LIUM, LST, Le Mans Université, France
- num: 153
  org: NA, University of Oxford, United Kingdom
- num: 154
  org: Department of Spanish, Western Michigan University, United States
- num: 155
  org: Department of Linguistics, University of California, Davis, United States
- num: 156
  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
- num: 157
  org: School of Information, University of Michigan, Ann Arbor, United States
- num: 158
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Norway

corrauth: "Timo B. Roettger"
email: "timo.b.roettger@iln.uio.no"
abstract: "Recent empirical studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior. In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question, resulting in substantial variability in reported effect sizes and their interpretation. Using Bayesian meta-analytic tools, we further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses. In light of this idiosyncratic variability, we recommend that researchers more transparently share details of their analysis, strengthen the link between theoretical construct and quantitative system and calibrate their (un)certainty in their conclusions"
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    template: template.tex
    includes:
      in_header: preamble.tex
---
